\documentclass[10pt,a4paper]{article}
%\documentclass[10pt,a4paper]{llncs}

\usepackage{makeidx}  % allows for indexgeneration
\usepackage[utf8]{inputenc}
\usepackage[cmex10]{amsmath}
\usepackage{amsfonts}
\usepackage{hyperref}
\usepackage{color}
\usepackage{cleveref}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{color}

\definecolor{gray}{rgb}{0.5,0.5,0.5}
\newcommand{\todo}[1]{{\color{red}\textsf{\textbf{TODO}}: #1}}
\newcommand{\uri}[1]{\texttt{#1}}
\newcommand{\word}[1]{`#1'}
\newcommand{\model}[1]{\textsf{#1}}
\newcommand{\copypaste}[1]{``{\color{gray}{#1}}''}
%\newcommand{\Cref}[1]{\ref{#1}}
\crefname{table}{Table}{Tables}

\title{Enhancing Named Entity Recognition and Disambiguation via Multilingual Data Fusion}
\author{TBD}
\date{\today}

\begin{document}
\maketitle

\begin{abstract}
\end{abstract}

\section{Introduction}

%===== DICAS ======
%- Digite uma frase por linha, assim fazer merge fica muito mais fácil com ferramentas de diff (tipo meld ou winmerge)
%- Sempre marque copy+paste com aspas e de preferencia com \verbatim{} ou \copypaste

Summary:
\begin{itemize}
\item pegamos tipos de outras línguas, avaliamos a acurácia da fusão. (10\% do valor do artigo)
\item usando tipos extendidos, extraímos um corpus de NER, treinamos e avaliamos.
\item reportamos que nossa cobertura com tipos extendidos melhorou.  (40\% do valor do artigo)
\item assuma-se portugues como língua sendo avaliada. usando sameAs, pegamos parágrafos de outras línguas (ex: Ingles), pegamos as entidades nos parágrafos em ingles, e pegamos os labels em portugues. 
avaliamos a eficacia de desambiguacao com o indice normal do portugues, e com o indice expandido com contexto do ingles. (50\% do valor do artigo)
\end{itemize}


\section{Related Work}

\paragraph{Data Fusion}
Data Fusion is... (quickly paraphrase from paper by Bleiholder and Naumann) - 1 paragraph

Wikipedia has cross-language links... allows us to complement one language with information from another.
Palmero et al. \copypaste{present a resource obtained by automatically mapping templates in 25 languages.} \cite{iknow13palmero}

Other authors have also worked on extending types...
Gangemi et al. present T\'{ipalo}, a tool that \copypaste{identifies the most appropriate types for an entity by interpreting its natural language definition, which is extracted from its corresponding Wikipedia page abstract.} \cite{iswc12gangemi}

%Classifying the Wikipedia Articles into the OpenCyc Taxonomy
%http://ceur-ws.org/Vol-906/paper2.pdf

\paragraph{Cross-language}
Cross-language entity linking is the problem ``where documents and named entities are in a different language than that used for the content of the reference knowledge base.''
Their \copypaste{best model achieves performance which is 94\% of a strong monolingual baseline.}
http://www.aclweb.org/anthology/I/I11/I11-1029.pdf

\todo{get/generate bibtex}
Cross Lingual Entity Linking with Bilingual Topic Model
Tao Zhang, Kang Liu and Jun Zhao
http://ijcai.org/papers13/Papers/IJCAI13-327.pdf

\todo{get/generate bibtex}
Analysis and Refinement of Cross-lingual Entity Linking
http://nlp.cs.rpi.edu/paper/clef2012.pdf

We are rather looking at complementing resource-poor languages. 
We use both ontology-derived and corpus-derived context.
We show that our best model actually improves the results.
We do not perform only entity-linking but the full annotation (NER+NEL)

\section{Methodology}

DBpedia exists in several languages...
Through sameAs links it maps between different chapters...
Types defined in one language can be transferred to other languages...
After expanding the type coverage, we can obtain a corpus from Wikipedia to train NER...

NER is not the whole story. Still need to disambiguate...
Some languages have fewer text available for training...
Corpus can also be used to expand corpus and train NEL systems cross-language...

\section{Experiments}


\subsection{Data Fusion Evaluation}

Did our strategy for expanding types worked? How many were right/wrong?

\subsection{NER Evaluation}

Evaluations on monolingual system obtained X\% precision and recall...
Cross-lingual improved?

\subsection{Cross-language Entity Linking Evaluation}

Evaluations on monolingual system obtained X\% precision and recall...
Cross-lingual improved?

\section{Conclusion}


\bibliographystyle{splncs03}
\bibliography{eswc}

\end{document}
